### 2012-09-06 inst/examples/figure3.Rmd
fix sdp calc: use z_m*z_g*f(y/z_m, q*z_i, p)

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3_det/", verbose=TRUE or`

@@

# Calculating the value of information

 Implements a numerical version of the SDP described in `r #knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty.

``` {r  setup, echo=FALSE, cache=FALSE}
# load required libraries
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())

theme_publish <- theme_set(theme_bw(14))
theme_publish <- 
  theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
        panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
        plot.background=theme_blank(), legend.title=theme_blank())

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`

@@

## Generate Figure 3 of Sethi et al. 2006

``` {r  setup, echo=FALSE, cache=FALSE}
# load required libraries
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
theme_publish <- theme_set(theme_bw(14))
theme_publish <- 
  theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
        panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
        plot.background=theme_blank(), legend.title=theme_blank())
